%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Professional Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

\cventry
{Infrastructure Team Lead}
{Genesis Automation}
{Cork, Ireland}
{Dec. 2021 - Present}
{
\begin{cvitems}
\item {Genesis Automation is a SME MedTech company that specializes in software solutions for hospitals, providing traceability, analytics, management and point of care solutions.}
\item {Working as an Infrastructure Lead, I am responsible for leading team, dictating workflow, adhering to SLAs, and assigning projects.}
\item {The focus is on tasks involving automation and improving cloud architecture.}
\item {Implemented DevOps methodologies and took initiative in introducing IaC, Terraform, Ansible, Packer, Boundary.}
\end{cvitems}
}

\cventry
{Cloud Infrastructure Engineer}
{Genesis Automation}
{Cork, Ireland}
{Oct. 2018 - Dec. 2021}
{
\begin{cvitems}
\item {I oversee our core infrastructures, networks, services, safeguards, and monitoring solutions. Providing 99.9\% uptime on system critical servers.}
\item {Developed deployment automation using Python and PowerShell for software upgrades on test and live systems}
\item {Designed and built public and private VPC networks for client solutions according to customer specifications.}
\item {Architected and developed high availability web applications infrastructure.}
\item {Containerized applications using Docker and managed ECR repositories.}
\item {Manage Amazon Web Services.}
\item {Took initiative in introducing and integrating IaC tools Packer, Terraform, and Ansible.}
\item {Setup network monitoring solutions and created visualization using flow logs, ELK stacks and Kibana.}
\item {Developed and automated backup and disaster recovery solutions for client production servers.}
\item {Introduced and maintained Vault high availability cluster using Consul backend storage cluster to manage organization-wise secrets.}
\end{cvitems}
}

\cventry
{Deskside Support Engineer} % Job title
{Ervia} % Organization
{Cork, Ireland} % Location
{Jan. 2017 - Oct. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Resolved end user incidents, logging, and recording through Service Now ticketing system.}
\item {Managed Exchange and Active Directory across multiple domains.}
\item {Spearheaded companywide project for the imaging, deployment, maintenance, and support in the migration of 300+ users from XenClient to Windows 10 laptops.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Deployment Engineer} % Job title
{PFH Technology Group} % Organization
{Cork, Ireland} % Location
{Dec. 2016 - Jan. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Coordinated and developed deployment process for rollout of laptops with Windows 7.}
\item {Trained team members in deployment and documentation process.}
\end{cvitems}
}

\end{cventries}
